### 2013-12-16 paper/main.tex
regulator system is wrong size?
An attempt was made to construct a regulator system
(Control Law, Full Order) however the sizes do not match.
The system (Gz) has one input and one output however the
feedback (K), as produced using Ackermann's Formula
has three inputs for the 3rd order system.
Is this a case where the other values must be estimated?

% {{{ Regulator Control System
\clearpage
\section{Regulator Control System}

What is needed is a regulator system where the input is applied
as torque.
The general system is shown in Figure \ref{fig:rpm1}.

% {{{ fig:rpm1, Regulator System
\begin{figure}[hbp!]
\begin{center}

@@

\end{center}
\caption{General system for regulating engine rpm.}\label{fig:rpm1}
\end{figure}
% }}}

>>>>

% {{{ Regulator Control System
\clearpage
\section{Regulator Control System, Control Law}

Instead of a servo system, which accepts a control input,
a regulator system can be constructed which tries to maintain
a single output value.  The general design is shown
in Figure \ref{fig:reg1}.

% {{{ fig:reg1, Regulator System
\begin{figure}[hbp!]
\begin{center}

@@

\end{center}
\caption{Regulator system for idle rpm control.}\label{fig:reg1}
\end{figure}
% }}}

One way to build this regulator system is to use the
Control Law Design\autocite[Pg. 280]{franklin1998digital}.
The block diagram of the system is shown in Figure \ref{fig:clff1}.

% {{{ fig:clff1
\begin{figure}[hpb!]
\begin{center}

	\node[gain]  	(Gz)	[] 	{$\begin{matrix}
									\dot{x} = Ax + Bu \\
										 y = Cx + Du
								 \end{matrix}$};
	\node[gain] 	(K)	[below=of Gz] 	{$-K$};

	 \draw [->]
	 		(Gz.east) -- ++(15mm,0)
			-| ++(0,-10mm)
			|- (K.east);

	 \draw [<-]
	 		(Gz.west) -- ++(-15mm,0)
			-| ++(0,-10mm)
			|- (K.west);

\end{tikzpicture}

\caption{Control Law system with full feedback.
It behaves as a regulator since not input is available.}
\label{fig:clff1}
\end{figure}
% }}}
